### 2022-07-25 src/text/2-package-subsections/modeling.tex
Update modeling  sub-package description

\subsection{gammapy.modeling}
\label{ssec:gammapy-modeling}
\todo{Quentin Remy}

\code{gammapy.modeling} contains all the functionality related to modeling and fitting
data. This includes spectral, spatial and temporal model classes, as well as
the fit and parameter API.

\subsubsection{Models}
\label{sssec:models}

The models are grouped into the following categories:

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves

\end{itemize}

@@

\todo{Add fit code example...}

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported Fit backend, including for example MCMC solutions.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}

>>>>

\subsection{gammapy.modeling}
\label{ssec:gammapy-modeling}
%
\code{gammapy.modeling} contains all the functionality related to modeling and fitting
data. This includes spectral, spatial and temporal model classes, as well as
the fit and parameter API.

\subsubsection{Models}
\label{sssec:models}
Source models in \gammapy are four dimensional models which support two
spatial dimensions $\ell, b$, and energy dimension $E$ as well as
the time dimension $t$. To simplify the the definition of the
models, \gammapy uses a factorised representation of the total source
model:

\begin{equation}
    f(l, b, E, t) = F(E)  \cdot G(l, b, E) \cdot  H(t, E)
\end{equation}

Where the spectral model $F$ implicitly carries the total flux
norm of the model. The spatial model $G$ optionally depends
on energy and allows to support e.g. energy dependent
morphology models. The temporal model component $H$
optionally also supports an energy variable to
allow for spectral variations of the model with time.

Following the factorisation The models objects are grouped
into the following categories:

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves
\end{itemize}

@@

\todo{Add fit code example...?}

The Fit class provides a uniform interface to multiple fitting backends:
“minuit”~\citep{iminuit}, “scipy”,~\citep{2020SciPy-NMeth}, and
“sherpa”~\citep{sherpa-2005,sherpa-2011}. Note that, for now, covariance matrix
and errors are computed only for the fitting with MINUIT. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported fitting backends, including for example MCMC solutions.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}
